Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-04-30 reviews/response.Rmd

A3. Aperiodic linear granularities are those that can not be defined by Definition 6. If $M_i$ is periodic, then $M = \bigcup M_i$ is periodic, but if each $M_i$'s are aperiodic, then $M$ could be periodic or aperiodic. In Definition 10, we want $M$ to be aperiodic. Definition 10 and introduction of Section 3.3 briefly rephrased to improve clarity.

Q4. $w$ in $T_w$ is not well defined for circular granularities in Section 3.2 & 3.5. The definition of $T_w$ uses $T_w$  itself in the formula making it hard to understand. Relevantly, what is the interpretation of $k$ where w = 0; 1; :::; k-1? In my opinion, the number of cycles
should be defined for cyclic granularities, for example, $w_{B,G}(z) = \lfloor z/P(B;G) \rfloor$, which
represent the cycle that the granule is in.

A4. Definition of $w$ and $R'$ included in Definition 9.

$T_w$ are the sets of indices of $B$ such that $G'(w) = \bigcup_{z \in T_w}B(z)$ does not use the definition of $T_w$. For example, if $B$ is `day` and $G'$ is `month`, then $G'(0) = {B(0)\cup B(1)\cup \dots \cup B(30)}$, $G'(1) = {B(31)\cup B(32)\cup \dots \cup B(58)}$ corresponding to January and February. Then $T_0 = \{0, 1, 2, \dots, 30\}$ and $T_1 = \{31, 32, \dots, 58\}$. If $z$ belongs to $k^{th}$ granule of $G'$, then $z \in T_k$. For example, if $z = 31$ then $z \in T_1$ and thus $k = 1$.

### 2021-04-30 main.Rmd
proof read viz

The basic plot choice for our data structure is one that can display distributions. For displaying the distribution of continuous univariate variable, many options are available. Displays based on descriptive statistics include box plots [@Tukey1977-jx] and its variation such as notched box plots [@McGill1978-hg] or other variations as mentioned in @Wickham2012-vr. They also include line or area quantile plots which can display any quantiles and not only quartiles like in a boxplot. Plots based on kernel density estimates include violin plots [@Hintze1998-zi], summary plot [@Potter2010-qc], ridge line plots [@R-ggridges], and highest density region (HDR) plots [@Hyndman1996-ft]. The less commonly used Letter-Value plots [@Hofmann2017-sg] is a midway between boxplots and density plots. Letter values are order statistics with specific depths. The median ($M$) divides the data set into halves. Each of the next letter values splits the remaining parts into two separate regions so that the fourths ($F$), eighths ($E$), sixteenths ($D$) etc. are obtained. They are useful for displaying the distributions beyond the quartiles specially for large data,
where boxplots mislabel data points as outliers.
One of the best approaches in exploratory data analysis is to draw a variety of plots to reveal information while keeping in mind the drawbacks and benefits of each of the plot choices. For example, boxplots obscure multimodality, and interpretation of density estimates and histograms may change depending on the bandwidth and bin widths respectively.

## Comparison across sub-groups induced by conditioning

@@

When $C_i$ is mapped to the $x$ position and $C_j$ to facets, then the $A_k$ levels are juxtaposed and each $B_\ell$ represent a group/facet. Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups. Hence, in this case the $A_k$s are compared against each other within each group. With the mapping of $C_i$ and $C_j$ reversed, the emphasis will shift to comparing $B_\ell$ levels rather than $A_k$ levels. For example, \autoref{fig:allFig}b shows the letter value plot across weekday/weekend partitioned by quarters of the year and \autoref{fig:allFig}c shows the same two cyclic granularities with their mapping reversed. \autoref{fig:allFig}b helps us to compare weekday and weekend within each quarter and \autoref{fig:allFig}c helps to compare quarters within weekend and weekday.

>>>>

The basic plot choice for our data structure is one that can display distributions. For displaying the distribution of continuous univariate variable, many options are available. Displays based on descriptive statistics include box plots [@Tukey1977-jx] and its variation such as notched box plots [@McGill1978-hg] or other variations as mentioned in @Wickham2012-vr. They also include line or area quantile plots which can display any quantiles and not only quartiles like in a boxplot. Plots based on kernel density estimates include violin plots [@Hintze1998-zi], summary plot [@Potter2010-qc], ridge line plots [@R-ggridges], and highest density region (HDR) plots [@Hyndman1996-ft]. The less commonly used Letter-Value plots [@Hofmann2017-sg] is a midway between boxplots and density plots. Letter values are order statistics with specific depths, for example, the median ($M$) is a letter value which divides the data set into halves. Each of the next letter values splits the remaining parts into two separate regions so that the fourths ($F$), eighths ($E$), sixteenths ($D$) etc. are obtained. They are useful for displaying the distributions beyond the quartiles specially for large data,
where boxplots mislabel data points as outliers.
One of the best approaches in exploratory data analysis is to draw a variety of plots to reveal information while keeping in mind the drawbacks and benefits of each of the plot choices. For example, boxplots might give an idea of the distribution at a glance while occupying less space by design, but they obscure multimodality.  Interpretation of density estimates and histograms may change depending on the bandwidth and bin widths respectively.

## Comparison across sub-groups induced by conditioning {#sec:aesthetics}

@@

When $C_i$ is mapped to the $x$ position and $C_j$ to facets, then the $A_k$ levels are juxtaposed and each $B_\ell$ represent a group/facet. Gestalt theory suggests that when items are placed in close proximity, people assume that they are in the same group because they are close to one another and apart from other groups. Hence, in this case the $A_k$'s are compared against each other within each group. With the mapping of $C_i$ and $C_j$ reversed, the emphasis will shift to comparing $B_\ell$ levels rather than $A_k$ levels. For example, \autoref{fig:allFig}b shows the letter value plot across weekday/weekend partitioned by quarters of the year and \autoref{fig:allFig}c shows the same two cyclic granularities with their mapping reversed. \autoref{fig:allFig}b helps us to compare weekday and weekend within each quarter and \autoref{fig:allFig}c helps to compare quarters within weekend and weekday.
